% Auto-converted from khan-exercises
\documentclass{article}
\usepackage{amsmath,amssymb}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\newcommand{\abs}[1]{\lvert #1\rvert}

\begin{document}
\section*{Average word problems}
\textbf{Question.} In his [[course(1)]] class, Alex took 5 [[plural\_form(exam(1), LENGTH)]].
                    His scores were [[toSentenceTex(SCORES)]].
                
                    In her [[course(1)]] class, Alex took 5 [[plural\_form(exam(1), LENGTH)]].
                    Her scores were [[toSentenceTex(SCORES)]].
                

                What was his average score on the [[plural\_form(exam(1))]]?
                What was her average score on the [[plural\_form(exam(1))]]?

\textbf{Answer.} 185.6

\textbf{Hints.}
\begin{itemize}
  \item The average is the sum of his scores divided by the number of scores.
  \item The average is the sum of her scores divided by the number of scores.
  \item There are 5 scores and their sum is [[SCORES.join(" + ")]] = 928.
  \item His average score is 928 \textbackslash\{\}div 5 = 185.6.
  \item Her average score is 928 \textbackslash\{\}div 5 = 185.6.
  \item Let his score on the next [[exam(1)]] be x.
  \item Let her score on the next [[exam(1)]] be x.
  \item The sum of all of his scores is then 5 $\cdot$ 84 + x.
  \item The sum of all of her scores is then 5 $\cdot$ 84 + x.
  \item The same sum must also be equal to 6 $\cdot$ 88.
  \item So, 5 $\cdot$ 84 + x = 6 $\cdot$ 88
  \item $\begin{aligned}
                    5 $\textbackslash\{\}cdot$ 84 + x &=& 6 $\textbackslash\{\}cdot$ 88 \\
                    420 + x &=& 528 \\
                    x &=& 528 - 420 \\
                    x &=& 203 \\
                    \end{aligned}$
  \item If he gets 100 on the remaining [[plural\_form(exam(1))]], the sum of his scores will be
                    5 $\cdot$ 84 + 3 $\cdot$ 100 = 928.
  \item If she gets 100 on the remaining [[plural\_form(exam(1))]], the sum of her scores will be
                    5 $\cdot$ 84 + 3 $\cdot$ 100 = 928.
  \item His overall average will then be 928 \textbackslash\{\}div 8 = 88.
  \item Her overall average will then be 928 \textbackslash\{\}div 8 = 88.
\end{itemize}
\end{document}
