% Auto-converted from khan-exercises
\documentclass{article}
\usepackage{amsmath,amssymb}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\newcommand{\abs}[1]{\lvert #1\rvert}

\begin{document}
\section*{Caesar cipher decryption}
\textbf{Question.} Alex is expecting to receive an encrypted message with the name of one of his classmates.
                        He knows the message will be encrypted with a Caesar cipher using a shift of 11.
                        When he returns to his desk, he finds a piece of paper with the following message on it:
                    
                        Alex is expecting to receive an encrypted message with the name of one of her classmates.
                        She knows the message will be encrypted with a Caesar cipher using a shift of 11.
                        When she returns to her desk, she finds a piece of paper with the following message on it:
                    
                    [[applyCaesar(M,SHIFT)]]
                    Help Alex crack the code, by typing the decrypted message in the answer box using all lowercase letters.

\textbf{Answer.} alex

\textbf{Hints.}
\begin{itemize}
  \item Since the message was encrypted by shifting each letter right by 11, to decrypt it we need to
                shift each letter left by 11.
  \item If we take the first letter [ and shift it left by 11,
                we get the letter a.
  \item If we take the second letter [ and shift it left by 11,
                we get the letter l.
  \item Continuing this for each letter, the decrypted message is: “alex”
\end{itemize}
\end{document}
