% Auto-converted from khan-exercises
\documentclass{article}
\usepackage{amsmath,amssymb}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\newcommand{\abs}[1]{\lvert #1\rvert}

\begin{document}
\section*{Congruent triangles 1}
\textbf{Question.} Are these two triangles congruent?

\textbf{Answer.} [[CHOICES[ANSWER]]]

\textbf{Hints.}
\begin{itemize}
  \item Triangles are congruent when all corresponding sides and interior angles are congruent.
  \item However, we do not need to know all the values in order to determine whether two triangles are congruent.
  \item The rules we use for determining congruency are SSS, ASA, SAS and AAS
  \item In this problem we are given the sides of the triangles, so we can compare them easily.
  \item Triangle B has 3 sides the same as triangle A, so they are congruent.
  \item Because the sides do not match, triangle B is not congruent with triangle A.
  \item In this problem we are given two sides and an angle between them, so we can use the SAS rule.
  \item Triangle B has those two sides and the angle the same as triangle A, so they are congruent.
  \item Because the sides and the angle do not match, triangle A is not congruent with triangle B.
  \item In this problem we are given two angles and as side between them, so we can use the ASA rule.
  \item Triangle B has those two angles and the side the same as triangle A, so they are congruent.
  \item Because the angles and the side do not match, triangle A is not congruent with triangle B.
  \item In this problem we are given two angles and another side so we can use the AAS rule.
  \item Triangle B has those two angles and the side the same as triangle A, so they are congruent.
  \item Because the angles and the side do not match, triangle A is not congruent with triangle B.
  \item In this problem we know all three triangle angles.
  \item However, having all three angles the same is not a property we can use to conclude that two triangles are congruent. We can only say for sure that they are similar.
                        
                        We do not have enough information to say that the two triangles are congruent.
  \item Because the angles do not match, triangle A is not congruent with triangle B.
\end{itemize}
\end{document}
