% Auto-converted from khan-exercises
\documentclass{article}
\usepackage{amsmath,amssymb}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\newcommand{\abs}[1]{\lvert #1\rvert}

\begin{document}
\section*{Counting 2}
\textbf{Question.} If 45 is the 1st number that Alex counts. what is the 15th number that he counts?

\textbf{Answer.} [[NUM\_COLORS * NUM\_POTS]]

\textbf{Hints.}
\begin{itemize}
  \item What is the first number that he counts?
  \item What is the first number that she counts?
  \item 45
  \item What is the second number that he counts?
  \item What is the second number that she counts?
  \item \textbackslash\{\}begin\{align*\}\&45 + 4 \textbackslash\{\}\textbackslash\{\}
                        \&= 49\textbackslash\{\}end\{align*\}
  \item What is the third number that he counts?
  \item What is the third number that she counts?
  \item \textbackslash\{\}begin\{align*\}\&45 + 4 + 4 \textbackslash\{\}\textbackslash\{\}
                        \&= 45 + (2 $\times$ 4) \textbackslash\{\}\textbackslash\{\}
                        \&= 53\textbackslash\{\}end\{align*\}
  \item What is the 15th number that he counts?
  \item What is the 15th number that she counts?
  \item \textbackslash\{\}begin\{align*\}\&45 + (14$\times$4) \textbackslash\{\}\textbackslash\{\}
                        \&= 45 + 56 \textbackslash\{\}\textbackslash\{\}
                        \&= [[NUM\_COLORS * NUM\_POTS]]\textbackslash\{\}end\{align*\}
  \item Given 5 people, each person shakes the hands of 4 other people.
  \item The following is almost the answer.
                        5 $\times$ 4 = 20
  \item We have double counted the handshakes though, since Alex shaking Alex's hand is the same handshake as Alex shaking Alex's hand.
  \item Therefore, the following is the correct answer.
                        $\frac{5 $\textbackslash\{\}times$ 4}{2}$ = [[NUM\_COLORS * NUM\_POTS]]
  \item If Alex decided on a flower color, how many different potted plant combinations are there?
  \item He can choose one of [[NUM\_POTS]] flower pots, and so there are [[NUM\_POTS]] different potted plants possible (given that he already chose a flower color).
  \item She can choose one of [[NUM\_POTS]] flower pots, and so there are [[NUM\_POTS]] different potted plants possible (given that she already chose a flower color).
  \item Since there are 2, 5 flower colors, there are 2, 5 $\times$ [[NUM\_POTS]] = [[NUM\_COLORS * NUM\_POTS]] possible potted plants.
\end{itemize}
\end{document}
