% Auto-converted from khan-exercises
\documentclass{article}
\usepackage{amsmath,amssymb}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\newcommand{\abs}[1]{\lvert #1\rvert}

\begin{document}
\section*{Fractions cut and copy 1}
\textbf{Question.} The starting block below is [[CODE\_PARENT]] unit long.
                    
                        The starting block below is [[CODE\_PARENT]] units long.
                    
                    
                        Use the tools below to convert the starting block into the goal block that is [[CODE\_OFFSPRING]] unit long.
                    
                        Use the tools below to convert the starting block into the goal block that is [[CODE\_OFFSPRING]] units long.
                    
                    The current block shows your progress.

\textbf{Answer.} Cut into: 1 piece
                            
                                
                                
                            
                        
                        
                            Copy: 1 time
                            
                                
                                
                            
                        
                    

                    
                        [pieces, times['current\_block']]
                    
                    
                        return roundTo(3, guess[1] / guess[0]) === roundTo(3, ANSWER);
                    
                    
                        pieces = guess[0];
                        times['current\_block'] = guess[1];
                        updateGraphAndAnswer();
                    
                    
                        $('#pieces').text(plural(guess[0], 'piece'));
                        $('\#current\_block\_times').text(plural(guess[1], 'time'));

\textbf{Hints.}
\begin{itemize}
  \item The starting block has a length of [[CODE\_PARENT]], which can be rewritten as:
                        \textbackslash\{\}qquad[[PARENT\_EXPANSION]]
                             + [[fraction(N\_PARENT - D, D\_PARENT)]] = 
                            [[fraction(N\_PARENT\_EXPANDED, D)]]
  \item The goal block has a length of [[CODE\_OFFSPRING]], which can be rewritten as:
                        \textbackslash\{\}qquad
                            
                                [[OFFSPRING\_EXPANSION]]
                                 + [[fraction(N\_OFFSPRING - D, D\_OFFSPRING)]] = 
                            
                            [[fraction(N\_OFFSPRING\_EXPANDED, D)]]
  \item [[fraction(N\_PARENT\_EXPANDED, D)]] is the same thing as
                        [[N\_PARENT\_EXPANDED]] $\times$ [[fraction(1, D)]].
  \item Therefore, if we cut the starting block into [[N\_PARENT\_EXPANDED]] equal pieces,
                        each piece will have a length of [[fraction(1, D)]] units.
  \item If we copy a piece [[N\_OFFSPRING\_EXPANDED]] times, we will get a length of
                        [[N\_OFFSPRING\_EXPANDED]] $\times$ [[fraction(1, D)]] = [[fraction(N\_OFFSPRING\_EXPANDED, D)]] units.
  \item Therefore the solution is to cut the starting block into [[N\_PARENT\_EXPANDED]] pieces
                        and copy the resulting block [[N\_OFFSPRING\_EXPANDED]] times.
\end{itemize}
\end{document}
