% Auto-converted from khan-exercises
\documentclass{article}
\usepackage{amsmath,amssymb}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\newcommand{\abs}[1]{\lvert #1\rvert}

\begin{document}
\section*{Fractions cut and copy 2}
\textbf{Question.} The starting block below is [[D\_PARENT === 1 ? N\_PARENT : mixedOrImproper(N\_PARENT, D\_PARENT)]] units long.
                    
                    Use the tools below to convert the starting block into both of the goal blocks that are
                    [[mixedOrImproper(N\_OFFSPRING\_1, D\_OFFSPRING\_1)]] units long and [[mixedOrImproper(N\_OFFSPRING\_2, D\_OFFSPRING\_2)]] units long.
                    The current blocks show your progress.

\textbf{Answer.} Cut Starting Block into: 1 piece
                            
                                
                                
                            
                        
                        
                            Copy Current Block 1: 1 time
                            
                                
                                
                            
                        
                        
                            Copy Current Block 2: 1 time
                            
                                
                                
                            
                        
                    

                    
                        [pieces, times['current\_block\_1'], times['current\_block\_2']]
                    
                    
                        var guess1 = roundTo(3, guess[1] / guess[0]),
                            guess2 = roundTo(3, guess[2] / guess[0]),
                            answer1 = roundTo(3, ANSWER\_1);
                            answer2 = roundTo(3, ANSWER\_2);
                        return guess1 === answer1 \&\& guess2 === answer2;
                    
                    
                        pieces = guess[0];
                        times['current\_block\_1'] = guess[1];
                        times['current\_block\_2'] = guess[2];
                        updateGraphAndAnswer();
                    
                    
                        guess = guess.length ? guess : [1, 1, 1];
                        $('#pieces').text(plural(guess[0], 'piece'));
                        $('\#current\_block\_1\_times').text(plural(guess[1], 'time'));
                        $('#current_block_2_times').text(plural(guess[2], 'time'));$

\textbf{Hints.}
\begin{itemize}
  \item We want to cut the starting block into a piece that can be copied into both goal block 1 and goal block 2.
  \item The least common denominator of 6 and 7
                        (the denominators of the goal blocks) is 20. Therefore you can copy a block
                        $\frac{1}{20}$ units long to make both goal blocks.
  \item The starting block has a length of [[D\_PARENT === 1 ? N\_PARENT : mixedOrImproper(N\_PARENT, D\_PARENT)]], which can be rewritten as:
                        \textbackslash\{\}qquad1 + $\frac{1}{3}$ = 
                            $\frac{4}{3}$
  \item We can rewrite the starting block length in terms of $\frac{1}{20}$ units:
                        \textbackslash\{\}qquad $\frac{4}{3}$ $\times$ 1 = 
                           $\frac{5}{4}$
  \item If we cut the starting block into 25 equal pieces,
                        each piece will have a length of $\frac{1}{20}$ units.
  \item Goal block 1 has a length of [[mixedOrImproper(N\_OFFSPRING\_1, D\_OFFSPRING\_1)]] units, which can be rewritten as:
                        \textbackslash\{\}qquad1 + $\frac{-1}{6}$ = 
                            $\frac{5}{6}$
  \item We can rewrite the goal block 1 length in terms of $\frac{1}{20}$ units:
                        \textbackslash\{\}qquad $\frac{5}{6}$ $\times$ 1 = 
                           1
  \item If we copy a piece of length $\frac{1}{20}$ units 20 times
                        we get 1 units, which is the length of goal block 1.
  \item We can rewrite the goal block 2 length in terms of $\frac{1}{20}$ units:
                        \textbackslash\{\}qquad $\frac{11}{7}$ $\times$ 1 = 
                           $\frac{11}{4}$
  \item If we copy a piece of length $\frac{1}{20}$ units 55 times
                        we get $\frac{11}{4}$ units, which is the length of goal block 2.
  \item Therefore the solution is to cut the starting block into 25 pieces, copy current block 1
                        20 times and current block 2
                        55 times.
\end{itemize}
\end{document}
