% Auto-converted from khan-exercises
\documentclass{article}
\usepackage{amsmath,amssymb}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\newcommand{\abs}[1]{\lvert #1\rvert}

\begin{document}
\section*{Parabola intuition 3}
\textbf{Question.} First, find the focus and directrix of the parabola by moving
                    the orange point and line to their correct positions. Then use that information to find the equation of the parabola.

\textbf{Answer.} [ graph.vertex.coord, graph.directrix.coordA[1] ] 
                        
                            if (\_.isEqual(guess, [[0, 1], -1])) \{
                                return "";
                            \}
                            return guess[0][0] === X1
                                \&\& guess[0][1] === Y1 + 1 / (4 * A)
                                \&\& guess[1] === Y1 - 1 / (4 * A)
                        
                        
                            graph.vertex.setCoord( guess[0] );
                            graph.directrix.coordA = [0, guess[1]];
                            graph.directrix.coordZ = [1, guess[1]];
                            graph.directrix.transform();
                        
                    

                    Focus: (0,\textbackslash\{\}quad1)
                    Directrix: y = \{\}-1
                    
                        Equation of the parabola:
                        y - \{\}-0.5\{\} = \{\}-0.5(x - \{\}-0.125)\textasciicircum{}2

\textbf{Hints.}
\begin{itemize}
  \item All points on a parabola are equidistant from the focus and directrix. There is only one place to put the orange focus point
                    and directrix line where this is true.
                    Show me
  \item The focus is ([[fractionReduce.apply(KhanUtil, toFraction(X1, 0.001))]],    [[fractionReduce.apply(KhanUtil, toFraction(VERTEX\_Y, 0.001))]])
                    and the directrix is y = [[fractionReduce.apply(KhanUtil, toFraction(DIR\_Y, 0.001))]]
  \item The equation for a parabola is y - y\_1 = a (x - x\_1)\textasciicircum{}2, where x\_1 and y\_1
                    are the coordinates of the vertex of the parabola (halfway between the focus and directrix).
  \item x\_1 is the same as the x coordinate of the focus.
                    y\_1 is at the midpoint of [[fractionReduce.apply(KhanUtil, toFraction(VERTEX\_Y, 0.001))]] and [[fractionReduce.apply(KhanUtil, toFraction(DIR\_Y, 0.001))]].
  \item So x\_1 = [[fractionReduce.apply(KhanUtil, toFraction(X1, 0.001))]].
                    And y\_1 = $\frac{[[fractionReduce.apply(KhanUtil, toFraction(VERTEX_Y, 0.001))]] + [[fractionReduce.apply(KhanUtil, toFraction(DIR_Y, 0.001))]]}{2}$ = [[fractionReduce.apply(KhanUtil, toFraction(Y1, 0.001))]].
  \item The leading coefficient a in the equation y - y\_1 = a (x - x\_1)\textasciicircum{}2 indicates how "wide" and
                    in what direction the parabola opens. It's always the reciprocal of 2 times the distance from the directrix to the focus.
  \item a = $\frac{1}{2 $\textbackslash\{\}times$ ([[fractionReduce.apply(KhanUtil, toFraction(VERTEX_Y, 0.001))]] {-}$ [[fractionReduce.apply(KhanUtil, toFraction(DIR\_Y, 0.001))]])\} = [[fractionReduce.apply(KhanUtil, toFraction(A, 0.001))]]
  \item So the equation of the parabola is y - [[fractionReduce.apply(KhanUtil, toFraction(Y1, 0.001))]] = [[fractionReduce.apply(KhanUtil, toFraction(A, 0.001))]](x - [[fractionReduce.apply(KhanUtil, toFraction(X1, 0.001))]])\textasciicircum{}2.
\end{itemize}
\end{document}
