% Auto-converted from khan-exercises
\documentclass{article}
\usepackage{amsmath,amssymb}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\newcommand{\abs}[1]{\lvert #1\rvert}

\begin{document}
\section*{Shifting and reflecting functions}
\textbf{Question.} What is \textbackslash\{\}red\{g(x)\} in terms of \textbackslash\{\}blue\{f(x)\}?

\textbf{Answer.} [["f(" + toFractionTex(Y\_COEFFICIENT) + "x)"]]

\textbf{Hints.}
\begin{itemize}
  \item Function \textbackslash\{\}red\{g(x)\} is shifted 0 units right relative to \textbackslash\{\}blue\{f(x)\}.
  \item This means the value of \textbackslash\{\}red\{g\} at a number x is the same as the value
                                of \textbackslash\{\}blue\{f\} at a number 0 less than x.
                            
                        
                        What would this sentence look like as an equation?
  \item g(x) = [["f(" + toFractionTex(Y\_COEFFICIENT) + "x)"]]
  \item Function \textbackslash\{\}red\{g(x)\} is shifted 0 units down relative to \textbackslash\{\}blue\{f(x)\}.
  \item Therefore, to find \textbackslash\{\}red\{g(x)\} you can find \textbackslash\{\}blue\{f(x)\}
                            and subtract 0.
  \item Therefore g(x) = [["f(" + toFractionTex(Y\_COEFFICIENT) + "x)"]].
  \item Function \textbackslash\{\}red\{g(x)\} is not flipped vertically compared to \textbackslash\{\}blue\{f(x)\},
                        so does not have a negative coefficient.
  \item Function \textbackslash\{\}red\{g(x)\} is stretched vertically relative to
                        
                        \textbackslash\{\}blue\{f(x)\},
                        so must be multiplied by a number with a magnitude greater than 1.
  \item Therefore g(x) = [["f(" + toFractionTex(Y\_COEFFICIENT) + "x)"]].
  \item Function \textbackslash\{\}red\{g(x)\} is flipped horizontally compared to \textbackslash\{\}blue\{f(x)\},
                            so we should multiply x by -1 reflect it over the y-axis.
                        
                        
                            This new function, \textbackslash\{\}green\{f(-x)\} is closer to \textbackslash\{\}red\{g(x)\}, but they are still not equal.
                            What else do we need to do?
  \item Function \textbackslash\{\}red\{g(x)\} is stretched horizontally relative to
                        \textbackslash\{\}green\{f(-x)\}
                        \textbackslash\{\}blue\{f(x)\},
                        so must be multiplied by a number with a magnitude less than 1.
  \item Function \textbackslash\{\}red\{g(x)\} is compressed horizontally relative to
                        \textbackslash\{\}green\{f(-x)\}
                        \textbackslash\{\}blue\{f(x)\},
                        so must be multiplied by a number with a magnitude greater than 1.
  \item Therefore g(x) = [["f(" + toFractionTex(Y\_COEFFICIENT) + "x)"]].
\end{itemize}
\end{document}
