% Auto-converted from khan-exercises
\documentclass{article}
\usepackage{amsmath,amssymb}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\newcommand{\abs}[1]{\lvert #1\rvert}

\begin{document}
\section*{Similar triangles 2}
\textbf{Question.} Which triangles are similar to triangle ABC?

\textbf{Answer.} <code>GHI</code>

\textbf{Hints.}
\begin{itemize}
  \item The sides of similar triangles are always proportional. This is known as 
                    \textbackslash\{\}color\{orange\}\{Side-Side-Side (SSS) Similarity\}.
  \item First, let's determine whether ABC and DEF are similar.
  \item In triangle DEF, DE = A, EF = [, and FD = [.
                    In triangle ABC, AB = r, BC = [, and CA = [.
  \item In order for ABC and DEF to be similar:
                    $\frac{AB}{\color{blue}$\{DE\}\} = $\frac{BC}{\color{blue}$\{EF\}\} = $\frac{CA}{\color{blue}$\{FD\}\}
  \item Substitute in the proper values for each side.
                    $\frac{r}{\color{blue}$\{A\}\} \textbackslash\{\}neq $\frac{[}{\color{blue}$\{[\}\} \textbackslash\{\}neq $\frac{[}{\color{blue}$\{[\}\}
  \item Since not all the proportions are equal, ABC is not similar to DEF.
  \item Since all the proportions are equal, ABC is similar to DEF.
  \item Next, let's determine whether ABC and GHI are similar.
  \item In triangle GHI, GH = A, HI = [, and IG = [.
                    In triangle ABC, AB = r, BC = [, and CA = [.
  \item For triangles ABC and GHI to be similar:
                    $\frac{AB}{\color{red}$\{GH\}\} = $\frac{BC}{\color{red}$\{HI\}\} = $\frac{CA}{\color{red}$\{IG\}\}
  \item Substitute in the proper values for each side.
                    $\frac{r}{\color{red}$\{A\}\} \textbackslash\{\}neq $\frac{[}{\color{red}$\{[\}\} \textbackslash\{\}neq $\frac{[}{\color{red}$\{[\}\}
  \item Since all the proportions are equal, ABC is similar to GHI.
  \item GHI is similar to ABC
                    DEF and GHI are similar to ABC
                    Neither DEF nor GHI are similar to ABC
\end{itemize}
\end{document}
