% Auto-converted from khan-exercises
\documentclass{article}
\usepackage{amsmath,amssymb}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\newcommand{\abs}[1]{\lvert #1\rvert}

\begin{document}
\section*{Identifying slope of a line}
\textbf{Question.} What is the slope of the line through the points ([[X1]], [[Y1]]) and ([[X2]], [[Y2]])?

\textbf{Answer.} [[(Y1 - Y2) / (X1 - X2)]]

\textbf{Hints.}
\begin{itemize}
  \item The slope of a line is the amount of change in the y-coordinate as the x-coordinate increases by one unit.
  \item The equation for the slope is:
                    \textbackslash\{\}qquad m = \textbackslash\{\}dfrac\{\textbackslash\{\}blue\{y\_2\} - \textbackslash\{\}purple\{y\_1\}\}\{\textbackslash\{\}blue\{x\_2\} - \textbackslash\{\}purple\{x\_1\}\}
  \item Substitute the values for
                            (\textbackslash\{\}purple\{[[X1]]\}, \textbackslash\{\}purple\{[[Y1]]\}) and
                            (\textbackslash\{\}blue\{[[X2]]\}, \textbackslash\{\}blue\{[[Y2]]\}):
                        
                        
                            \textbackslash\{\}qquad m = \textbackslash\{\}dfrac\{\textbackslash\{\}blue\{[[Y2]]\} - \textbackslash\{\}purple\{[[negParens(Y1)]]\}\}
                            \{\textbackslash\{\}blue\{[[X2]]\} - \textbackslash\{\}purple\{[[negParens(X1)]]\}\} =
                            \textbackslash\{\}dfrac\{\textbackslash\{\}green\{[[Y2 - Y1]]\}\}\{\textbackslash\{\}pink\{[[X2 - X1]]\}\}
  \item So, the slope m is [[fractionReduce( Y2 - Y1, X2 - X1 )]].
  \item A slope of [[M.display]] means that the y-coordinate changes by [[M.display]]
                    as the x-coordinate increases by one unit.
  \item The \textbackslash\{\}color\{[[COLORS[WHICH].hex]]\}\{\textbackslash\{\}text\{[[COLORS[WHICH].name.toLowerCase()]]\}\}
                        graph has a slope of [[M.display]].
                        The other graphs have slopes of [[toSentence(OTHER\_SLOPES)]].
  \item A slope of [[M.display]] means the
                    y-coordinate doesn't change at all as the x-coordinate changes.
  \item A vertical line has an undefined slope.
                    The x-coordinate doesn't change,
                    so if we try to calculate the slope between two points with
                    m = \textbackslash\{\}dfrac\{\textbackslash\{\}blue\{y\_2\} - \textbackslash\{\}purple\{y\_1\}\}\{\textbackslash\{\}blue\{x\_2\} - \textbackslash\{\}purple\{x\_1\}\},
                    we'll have to divide by zero!
  \item The \textbackslash\{\}color\{[[COLORS[WHICH].hex]]\}\{\textbackslash\{\}text\{[[COLORS[WHICH].name.toLowerCase()]]\}\}
                    graph depicts an undefined slope.
  \item The \textbackslash\{\}color\{[[COLORS[WHICH].hex]]\}\{\textbackslash\{\}text\{[[COLORS[WHICH].name.toLowerCase()]]\}\}
                    graph depicts a slope of [[M.display]].
\end{itemize}
\end{document}
