% Auto-converted from khan-exercises
\documentclass{article}
\usepackage{amsmath,amssymb}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\newcommand{\abs}[1]{\lvert #1\rvert}

\begin{document}
\section*{Vigenere cipher encryption}
\textbf{Question.} Alex wants to encode the following cryptic message:
                    [["The " + animal( 1 ) + " wears " + an(color(1)) + " " + clothing(1)]]
                    
                        In an effort to increase security, Alex decides to encrypt it with a Vigenere cipher
                        using his own name as the keyword. What will the secret message look like once it is encrypted?
                    
                        In an effort to increase security, Alex decides to encrypt it with a Vigenere cipher
                        using her own name as the keyword. What will the secret message look like once it is encrypted?

\textbf{Answer.} [[applyVigenere(M,person(1))]]

\textbf{Hints.}
\begin{itemize}
  \item First, we need to convert every letter in the keyword to a number.
            Where a\{\} = 0 and z\{\} = 25.
  \item For our keyword Alex the first few letters convert to: 
                \textbackslash\{\}quad\textbackslash\{\}begin\{align\}
                    \textbackslash\{\}text\{A\} \&: 0 \textbackslash\{\}\textbackslash\{\}
                    \textbackslash\{\}text\{l\} \&: 11 \textbackslash\{\}\textbackslash\{\}
                    \textbackslash\{\}text\{e\} \&: 4
                    \textbackslash\{\}end\{align\}
  \item To encrypt our message, shift the first letter in the message to the right by the letter/value
                of the first letter in our keyword.
  \item In this case, we shift the letter [ by the value
                0
                which results in the letter
                [["abcdefghijklmnopqrstuvwxyz"[("abcdefghijklmnopqrstuvwxyz".indexOf(M[0].toLowerCase()) + "abcdefghijklmnopqrstuvwxyz".indexOf(person(1)[0].toLowerCase()) ) \% 26]]].
  \item We do the same with the second letter of the message, and the second letter of the keyword.
                Shift the letter [ by the value 11
                which results in the letter k.
  \item Every time we reach the last letter of the keyword, we can go back to the first letter of the keyword to continue encrypting the rest of the message.
  \item Be sure to ignore spaces in the message.
  \item The encrypted message is “[[applyVigenere(M,person(1))]]”
\end{itemize}
\end{document}
